---
title: "p8105_hw1_yh3822"
output: github_document
date: "2024-09-19"
---

```{r setup}
library(palmerpenguins)
library(ggplot2)
library(tidyverse)
```


## Problem 1


```{r}
data("penguins", package = "palmerpenguins")
penguins_df = penguins
```

```{r}
skimr::skim(penguins_df)
```



This dataset has `r nrow(penguins_df)` rows and `r ncol(penguins_df)` columns, which means there are totally `r nrow(penguins_df)` subjects and `r ncol(penguins_df)` variable names, including species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. There are also some missing values in sex, bill_length_mm, bill_depth_mm, flipper_length_mm, and body_mass_g.

The mean of flipper_length is `r mean(penguins_df$flipper_length_mm, na.rm = TRUE)`.


```{r, warning=FALSE, message=FALSE}
ggplot(penguins_df, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.png")
```


## Problem 2


```{r}
random_sample = rnorm(10)
logical_vector = random_sample > 0
character_vector = letters[1:10]
factor_vector = factor(rep(c("level1", "level2", "level3"), length.out = 10))
```

```{r, warning=FALSE, message=FALSE}
sample_df = data_frame(random_sample, logical_vector, character_vector, factor_vector)
sample_df
```

```{r}
mean(sample_df %>% pull(random_sample))
mean(sample_df %>% pull(logical_vector))
mean(sample_df %>% pull(character_vector))
mean(sample_df %>% pull(factor_vector))
```
The random sample works, and logical vector works with a warning. Both character vector, and factor vector do not work.




